---
title: "EDA ON WALMART DATASET"
author: "TEAM PROJECT"
date: "2022-10-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
library(readxl)
library(RColorBrewer)
library(ggplot2)
getwd()
data = read_excel("Walmart Retail Dataset.xlsx")
View(data)
str(data)
head(data)
```

```{r}
data$`Customer Age`[is.na(data$`Customer Age`)]= mean(data$`Customer Age`,na.rm = T)
data$`Product Base Margin`[is.na(data$`Product Base Margin`)]=mean(data$`Product Base Margin`,na.rm = T)
View(data)
```

## CUSTOMER SEGMENT
```{r}
CS_OP =table(data$`Customer Segment`,data$`Order Priority`)
summary(CS_OP)
CS_PSC = table(data$`Customer Segment`,data$`Product Sub-Category`)
summary(CS_PSC)
CS_PSC
CS_PC = table(data$`Customer Segment`,data$`Product Category`)
summary(CS_PC)
CS_SM = table(data$`Customer Segment`,data$`Ship Mode`)
summary(CS_SM)
CS_REGION = table(data$`Customer Segment`,data$Region)
summary(CS_REGION)
```

**Performed chi-sq test between Customer Segment and other variables.**
**Inference drawn is that all the fields are independent.**


## ORDER_PRIORITY
```{r}
OP_PC = table(data$`Order Priority`,data$`Product Category`)
summary(OP_PC)
OP_PCon = table(data$`Order Priority`,data$`Product Container`)
summary(OP_PCon)
OP_PSC = table(data$`Order Priority`,data$`Product Sub-Category`)
summary(OP_PSC)
OP_SM = table(data$`Order Priority`,data$`Ship Mode`)
summary(OP_SM)
OP_REGION = table(data$`Order Priority`,data$Region)
summary(OP_REGION)
```

**Inference drawn is that all the fields are independent.**


## PRODUCT CATEGORY
```{r}
PC_PCon = table(data$`Product Category`,data$`Product Container`)
summary(PC_PCon)
PC_PSC = table(data$`Product Category`,data$`Product Sub-Category`)
summary(PC_PSC)
PC_SM = table(data$`Product Category`,data$`Ship Mode`)
summary(PC_SM)
PC_REGION = table(data$`Product Category`,data$Region)
summary(PC_REGION)
```

**Inference : The first three variables are dependent while region is independent of field product category.**


## PRODUCT CONTAINER
```{r}
PCON_PSC = table(data$`Product Container`,data$`Product Sub-Category`)
summary(PCON_PSC)
PCON_REGION = table(data$`Product Container`,data$Region)
summary(PCON_REGION)
PCON_SM = table(data$`Product Container`,data$`Ship Mode`)
summary(PCON_SM)
```

**Inference : Fields are dependent of each other.**


## PRODUCT SUB-CATEGORY
```{r}
PSC_REGION = table(data$`Product Sub-Category`,data$Region)
summary(PSC_REGION)
PSC_SM = table(data$`Product Sub-Category`,data$`Ship Mode`)
summary(PSC_SM)
SM_REGION = table(data$`Ship Mode`,data$Region)
summary(SM_REGION)
```

**Inference : Fields are independent of each other.**


## CORRELATION_TEST
## SALES
```{r}
cor(data$Sales,data$Discount)
cor(data$Sales,data$`Order Quantity`)
cor(data$Sales,data$Profit)
cor(data$Sales,data$`Shipping Cost`)
cor(data$Sales,data$`Product Base Margin`)
```

**Inference : Discount is slightly negative correlated whlie other variables are slightly positive correlated.**


## PROFIT
```{r}
cor(data$Profit,data$Discount)
cor(data$Profit,data$Sales)
cor(data$Profit,data$`Shipping Cost`)
```

**Inference : Sales and Profit are dependent on each other.**


## ORDER QUANTITY
```{r}
cor(data$`Order Quantity`,data$Discount)
cor(data$`Order Quantity`,data$Profit)
cor(data$`Order Quantity`,data$Sales)
cor(data$`Order Quantity`,data$`Shipping Cost`)
```

**Inference : Profit and Sales are dependent on Order Quantity.**


## DATA VISUALIZATION
```{r}
barplot(table(data$`Order Quantity`),col = "SKYBLUE",border = "WHITE",xlab = "ORDER QUANTITY",ylab = "Frequency of Order Quantity")
barplot(table(data$`Customer Segment`),col = "steelblue",border = "black",xlab = "Customer Segment",ylab = "Frequency")
barplot(table(data$Discount),col = rainbow(18),xlab = "Discount",ylab = "Frequency of Discount")
barplot(table(data$`Order Priority`),col = brewer.pal(5,"Dark2"),xlab = "Order Priority",ylab = "Frequncy of Order Priority")
```

```{r}
barplot(table(data$`Product Base Margin`),col=brewer.pal(5,"Paired"),xlab = "Product Base Margin",ylab = "Frequency of PBM")
barplot(table(data$`Product Category`),col = brewer.pal(5,"Blues"),xlab = "Product Category",ylab = "Frequency of Product Category")
barplot(table(data$`Product Sub-Category`),col = brewer.pal(6,"PRGn"),xlab = "Product Sub-Category",ylab = "Frequency of PSC")
```

```{r}
ggplot(data = data,aes(y = `Product Base Margin`,x = `Product Category`))+geom_point(col=2)
```

**Inference : Product Base Margin for the office supplies is higher followed by Technology and Furniture.**

```{r}
ggplot(data = data,aes(y = `Sales`,x = `Product Sub-Category`))+geom_point(col=7)+
theme(axis.text.x=element_text(size=15, angle=90,hjust=0.95,vjust=0.2))+
  coord_flip()

```

**Inference : Sales for Office Machines is higher which lies under office supplies category followed by Copiers and Fax, Bookcases and so on.**


```{r}
ggplot(data = data,aes(y = `Profit`,x =`Region`))+ geom_area(col="purple")
```

**Inference : Central region has the highest profit followed by west, south and east.**


```{r}
ggplot(data = data,aes(y = `Profit`,x = `Ship Mode`))+geom_point(col="blue")+coord_flip()
```

**Inference : Profit for the Regular Air is higher followed by Delivery truck and Express air.**


```{r}
ggplot(data = data,aes(y = `Shipping Cost`,x = `Region`))+ geom_boxplot(fill="orange",col="red")
```

**Inference : For central region shippinmg cost is higher whereas for the south region it is lowest.**


```{r}
ggplot(data = data,aes(y = `Profit`,x = `Product Container`))+geom_polygon(col = "darkgreen")
```

**Inference : Profit for the Large Box is highest, followed by jumbo drum, small box, jumbo box and so on.**


```{r}
ggplot(data = data,aes(y = `Shipping Cost`,x = `Order Priority`))+geom_point(col="brown")+
  coord_flip()
```

**Inference : As per the Order priority the shipping cost also varies, it is highest for critical and lowest for medium.**


